Comparing Machine Learning algorithms for classifying cognitive states from fMRI data

### 2012-11-10 article/article.tex
results

When PCA is used for feature extraction, the performance of Naive Bayes is significantly lower than when other feature selection methods are used. By using an exact binomial test we found out the confidence interval of this result

We can also distinguish the fact that when different structure is used for the data, the performance increases, though not significantly. For example, in the case of the Naive Bayes classifier when different structure is used, its performance increases approximately 4\%.

>>>>

From Table~\ref{tab:results} we can distinguish the fact that when PCA is used for feature extraction, the performance of Naive Bayes is lower than when other feature selection methods are used. By using an exact binomial test we found out that the confidence interval of the predictive performance of Naive Bayes when PCA is used is $95\% CI: 56.9 - 65.8$.

We can also distinguish the fact that when different structure is used for the data, the performance increases,
